A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network

### 2014-12-11 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
adicao de detalhes do simulador.

In order to evaluate the proposed technique, simulations were performed in scenarios based on real street maps exported from the OpenStreetMap (OSM) data set, which is an open collaborative mapping project \citep{OSM}. The scenarios have been chosen to cover a wide range of possible street layouts. They have been populated with nodes with an average distance of $40m$, in order to simulate a real street lighting system, with network sizes ranging from 100 up to 400 nodes. A sample of the chosen scenarios are shown in figure \ref{sim_scenarios}.

For every scenario, there were generated $1000$ random source-destination pairs, giving a coverage of up to $10$\% of the possible source-destination combinations. Also, every simulation was performed for $10$ different (random) positions of the DODAG root in every scenario, which gives a good coverage of the $5$ possible root placements (i.e. center and top/bottom-right/left corners). Then, for the each source-destination pair, the route was determined by each algorithm under test (RPL, GOAFR, \textit{GeoRank} and Dijkstra' algorithm for shortest path) and length of each route was measured in number of hops. The average length of the routes was computed and the results are shown in figure \ref{sim_results} \rev{with 95\% confidence intervals}.

>>>>

In order to evaluate the proposed technique, simulations were performed in scenarios based on real street maps exported from the OpenStreetMap (OSM) data set, which is an open collaborative mapping project \citep{OSM}. \rev{The simulator, written in Julia, is based on an idealistic MAC/PHY layer with disc model for radio propagation}. The scenarios have been chosen to cover a wide range of possible street layouts \rev{inside a square region}. They have been populated with nodes with an average distance of $40m$, in order to simulate a real street lighting system, with network sizes ranging from 100 up to 400 nodes. A sample of the chosen scenarios are shown in figure \ref{sim_scenarios}.

For every scenario, there were generated $1000$ random source-destination pairs, giving a coverage of up to $10$\% of the possible source-destination combinations. \rev{For the RPL, the DAG is constructed as the Breadth First Search (BFS) tree for the topology, thus the expected transmission count (ETX) equals one for the preferred parent}. Also, every simulation was performed for $10$ random positions of the DODAG root in every scenario, which gives a good coverage of the \rev{root placements in a square region} \sout{$5$ possible root placements (i.e. center and top/bottom-right/left corners)}, \rev{and accounts for the unpredictability in the root location due to several factors, such as the availability of infrastructure (e.g. internet connection),  future network scaling, etc}. Then, for the each source-destination pair, the route was determined by each algorithm under test (RPL, GOAFR, \textit{GeoRank} and Dijkstra' algorithm for shortest path) and length of each route was measured in number of hops. The average length of the routes was computed and the results are shown in figure \ref{sim_results} \rev{with 95\% confidence intervals}.
